### 2024-04-29 thesis/input_files/literaturereview.tex
comm 2.1 2.2

This section presents the results of the bibliometric analysis we performed on March 6th 2024. This survey has been carried out by using the Scopus citation database. For details on the specific queries entered in Scopus, refer to \ref{src_code}.

@@

To get started, let us consider the evolution of the EF field over the years. This is visualized in figure \ref{fig:epf_evolution}, with results grouped by category; note, articles prior to the 2000 have been aggregated together due to their small number. Figure \ref{fig:epf_evolution} shows the trend of an increasing interest in EF.

@@

The next question was to compare the state of point versus probabilistic forecasting, this is visualized in figure \ref{fig:point_vs_prob}. What it can be concluded is that probabilistic is less developed than point forecasting. To our mind this is due to the complexity of probabilistic forecast.

@@

  \caption{Point versus probabilistic pubblications}

@@

The EF literature is dominated by statistical and computational intelligence methods as can be seen from figure \ref{fig:cs_stat_both}, with CI methods beign slightly preferred. 

@@

  \caption{Pubblications by method}

@@

EF is an heterogenous field of research, its researchers come from a wide array of backgrounds, with electrical engineers and statisticians making up the top contributors; their different educational training may explain why the split between statistical and computational intelligence methods is so marked. Figure \ref{fig:subject_area} depitcs the EF publications by subject area. What can be concluded, is that the bulk of pubblications come from engineering, computer science, mathematics and econometrics.

@@

  \includegraphics[width=\textwidth]{images/subject_area.jpg}

@@

Finally, in order to refer to the most relevant source in the field, EF outlets have been ranked by popularity and plotted in figure \ref{fig:src_title}.

@@

  \includegraphics[width=\textwidth]{images/src_title.jpg}

>>>>

This section presents the results of the bibliometric analysis we performed on March 6th 2024. This survey has been carried out by using the Scopus citation database. For details on the specific queries entered in Scopus, refer to Subsection 5 of the Appendix \ref{src_code}.

@@

To get started, let us consider the evolution of the EF field over the years. This is visualized in Figure \ref{fig:epf_evolution}, with results grouped by category. Articles prior to the 2000 have been aggregated together due to their small number. Figure \ref{fig:epf_evolution} shows the trend of an increasing interest in EF.

@@

The next question is to compare the state of point versus probabilistic forecasting, this is visualized in Figure \ref{fig:point_vs_prob}. What can be concluded is that probabilistic is less developed than point forecasting. To our mind this is due to the complexity of probabilistic forecasts.

@@

  \caption{Point versus probabilistic pubblications over the past years}

@@

The EF literature is dominated by statistical and computational intelligence (CI) methods as can be seen from Figure \ref{fig:cs_stat_both}, with CI methods being slightly preferred. 

@@

  \caption{Pubblications by method over the past years}

@@

EF is a heterogenous field of research, its researchers come from a wide array of backgrounds, with electrical engineers and statisticians making up the top contributors; their different educational training may explain why the split between statistical and computational intelligence methods is so marked. Figure \ref{fig:subject_area} depitcs the EF publications by subject area. What can be concluded, is that the bulk of pubblication come from engineering, computer science, mathematics and econometrics.

@@

  \includegraphics[width=\textwidth]{images/subject_area.png}

@@

In order to refer to the most relevant source in the field, EF outlets have been ranked by popularity and plotted in Figure \ref{fig:src_title}.

@@

  \includegraphics[width=\textwidth]{images/src_title.png}
